---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# zoabeta: An R package for the zero-one-augmented beta distribution

<!-- badges: start -->
<!-- badges: end -->

The zoabeta package is a very simple implementation of the zero-one-augmented
beta distribution that supports values on the unit interval (e.g. proportions or
probabilities) that might include zero or one values, in contrast to the
standard beta distribution which does not support zero or one values. The
package provides density, probability, quantile and random variate functions
analogous to the standard beta distribution functions in the R `stats` package.

## Installation

You can install the development version of zoabeta from [GitHub](https://github.com/) with:

``` r
# Using the pak package
# install.packages("pak")
pak::pak("mbedward/zoabeta")

# Or using the remotes package
# install.packages("remotes")
remotes::install_github("mbedward/zoabeta")
```

## Examples

Generate random values:

```{r example}
library(zoabeta)

# Generate random values where there is a 0.2 probability of zero and a 
# 0.1 probability of one, with intermediate values following a beta(2, 5) 
# distribution

x <- rzoabeta(n = 1e4, shape1 = 2, shape2 = 5, pzero = 0.2, pone = 0.1)
hist(x, breaks = 40)

```

